---
title: "Documentation of R package"
author: "Andreas Grosser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r, echo = FALSE, include = FALSE}
library(Farsdata)
library(dplyr)
library(maps)
```

This vignette is a brief overview of the Farsdata package and its functionality. It provides some useful functions for its analysis.

## Exported functions
 
Three functions are exported so that the user can use them

- `fars_read()`
- `fars_summarize_years()`
- `fars_map_state()`

Furthermore I desscribe how the functions works. I am using the FARS data files 2013-2014 which can be found in the directory Farsdata.

## FARS Read function

The function `fars_read()` reads a data file from a path (as argument). It returns a loaded data set.

```{r fars_read_example}
filename <- system.file("extdata/accident_2013.csv.bz2", package = "Farsdata")
fars_read(filename)
```

## FARS Summarize function

The function `fars_summarize_years()` takes a vector/ list of years as an argument and returns a tables of accidents per month and year.

```{r fars_summarize_years_example}
setwd(system.file("extdata", package = "Farsdata"))
fars_summarize_years(2013:2014)
```

## FARS Map state

The function `fars_map_state()` takes a state and a year as inputs and returns a plot of the state and its accident locations.

```{r fars_map_state_example}
setwd(system.file("extdata", package = "Farsdata"))
fars_map_state(45, 2014)
```
